Stability in human interaction networks: primitive typology of vertex, prominence of measures and time activity statistics

### 2015-04-18 paper.tex
pequenas melhoras

Each time scale also revealed patterns through histograms in Tables~\ref{tab:hin},~\ref{tab:win},~\ref{tab:min} and~\ref{tab:min2}. The exceptions of the seconds, minutes and years scales received dedicated Sections~\ref{sec:secmin} and~\ref{sec:years}.

@@

\begin{table}[!h]
	\caption{Principal components formation with symmetry-related metrics (see Section~\ref{measures}). MET list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. In this case, clusterization is pushed to the third principal component. The second component is primarily derived from symmetry measurements, but also out-degree and out-strength, and disequilibrium standard deviation. Betweenness centrality again has a role similar to degree, but weaker. The clusterization component combines with disequilibrium, while asymmetry is combined to out-degree and out-strength. The three components have in average 80.36\% of the variance.}
	\footnotesize
	\input{tables/tabPCA3LAU}
\label{tab:pcain}
\end{table}

>>>>

Time scale also revealed patterns through histograms as exposed in Tables~\ref{tab:hin},~\ref{tab:win},~\ref{tab:min} and~\ref{tab:min2}. Seconds, minutes and years scales received the dedicated Sections~\ref{sec:secmin} and~\ref{sec:years} instead of tables.

@@

\begin{table}[!h]
	\caption{Principal components formation with symmetry-related metrics (see Section~\ref{measures}). MET list, $ws=1000$ messages in 20 disjoint positioning was used for statistics. In this case, clusterization is pushed to the third principal component. The second component is primarily derived from symmetry measurements, but also out-degree and out-strength, and disequilibrium standard deviation. Betweenness centrality again has a role similar to degree, but weaker. The clusterization component combines with disequilibrium, while asymmetry is combined to out-degree and out-strength. The three components have in average 80.36\% of the variance.}
	\footnotesize
	\input{tables/tabPCA3CPP}
\label{tab:pcain}
\end{table}
